---
title: "Homework Week 9 - NYT APIs"
author: "Robert_M"
date: "October 28, 2018"
output: 
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Assignment - New York Times APIs {.tabset .tabset-pills}

The New York Times web site provides a rich set of APIs, as described here: [http://developer.nytimes.com/docs] http://developer.nytimes.com/docs
You'll need to start by signing up for an API key.  Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

# Load packages/libraries 
```{r}
library(jsonlite)
library(httr)
library(RCurl)
```


## Reading in movie review API
```{r}
url <- GET("https://api.nytimes.com/svc/movies/v2/reviews/search.json", query = list(api_key = "e6151b6f4d364acf8d6e5d8af9ef7072"))
url

APIMovie <- fromJSON("https://api.nytimes.com/svc/movies/v2/reviews/search.json?api_key=e6151b6f4d364acf8d6e5d8af9ef7072") 
APIMovie_table <- as.data.frame(APIMovie)
APIMovie_table
```

## Reading in article search API
```{r}
url <- GET("https://api.nytimes.com/svc/search/v2/articlesearch.json", query = list(api_key = "e6151b6f4d364acf8d6e5d8af9ef7072"))
url

APIArticle <- fromJSON("https://api.nytimes.com/svc/search/v2/articlesearch.json?api_key=e6151b6f4d364acf8d6e5d8af9ef7072") 
APIArticle_table <- as.data.frame(APIArticle)
APIArticle_table
```

## Reading in top stories API
```{r}
url <- GET("http://api.nytimes.com/svc/topstories/v2/home.json", query = list(api_key = "e6151b6f4d364acf8d6e5d8af9ef7072"))
url

APITopStories <- fromJSON("http://api.nytimes.com/svc/topstories/v2/home.json?api_key=e6151b6f4d364acf8d6e5d8af9ef7072") 
APITopStories_table <- as.data.frame(APITopStories)
APITopStories_table
```

```{r}

```

